\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{braket}
\usepackage{booktabs} 
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{xcolor}
\usepackage{float}
\usepackage{hyperref}
\usepackage[title]{appendix}

%%% 
% Define new style of sections
%%%
\titleformat*{\section}{\LARGE\bfseries}
\titleformat*{\subsection}{\Large\bfseries}
\titleformat*{\subsubsection}{\large\bfseries}
\titleformat*{\paragraph}{\large\bfseries}
\titleformat*{\subparagraph}{\large\bfseries}
%%%
% Title page
%%%
\title{
\begin{flushleft}
\rule{\textwidth}{1pt}\\
  \textsc{\textbf{The SEIQRS mathematical model adapted to the covid-19 virus oubreak in Lombardy}}\\[2mm]
\textsc{\large Paolo Sabatini}\\
\rule{\textwidth}{1pt}
  \end{flushleft}
}
%\author{
%\begin{flushleft} 
%\textsc{Paolo Sabatini} 
%\end{flushleft} 
%}

\date{}


 
\begin{document}

\maketitle


\begin{abstract}
This document uses the mathematical model Susceptible-Exposed-Infected-Quarantined-Recovered-Susceptible (SEIQRS) in the Small-World approximation. This mathematical framework is used to describe the outbreak of the COVID-19 in Italy, in particular in the most affected region, the Lombardy. To achieve a correct description of the data, the model is slightly modified. The interactions between people are modulated against time to mimic the social-distancing. Moreover corrections based on the number of performed tests are implemented. The model parameters are then measured through Profile Likelihood Fit against data of the oubreak in Lombardy. The fitted parameters are the used to create a baseline simulation of the oubreak and to provide estimations of the outbreak features. These features are then also validated against the actual evolution of the virus. The model provides a robust estimation of the evolution in particular of their shape and evolution. Estimations of the absolute numbers are affected by the large errors due to the fit on a limited time (until April 4th).

\end{abstract}
\vspace{2cm}
\tableofcontents

\newpage

\input{sections/Introduction}
\input{sections/ModelDescription}
\input{sections/Dataset}
\input{sections/Covid19}
\input{sections/Conclusions}


\begin{thebibliography}{9}
\bibitem{MingLiu} 
Z.~Gao, M.~Liu and Y.~Xiao, 
\textit{Modeling and Analysis of Epidemic Diffusion within Small-World Network},
Journal of Applied Mathematics (2012) 841531.

\bibitem{MingLiuOld} 
M.~Liu and L.~Zhao, 
\textit{Analysis for epidemic diffusion and emergency demand in an anti-bioterrorism
system},
International Journal of Mathematical Modelling and Numerical Optimisation (2011), vol. 2, no. 1, pp. 51–68.

\bibitem{COVID-Clinical} 
Jiang, F., Deng, L., Zhang, L. et al., \emph{ Review of the Clinical Characteristics of Coronavirus Disease 2019 (COVID-19)}, J GEN INTERN MED (2020).

\bibitem{Lab24}
Il Sole 24 Ore,
\textit{ 
Coronavirus in Italia, i dati e la mappa},
\href{https://lab24.ilsole24ore.com/coronavirus/}{https://lab24.ilsole24ore.com/coronavirus/}

\bibitem{WHO}
World Health Organisation, \emph{Coronavirus disease 2019 (COVID-19)}, \href{https://www.who.int/docs/default-source/coronaviruse/situation-reports/20200414-sitrep-85-covid-19.pdf?sfvrsn=7b8629bb_4}{Situation report, 85.}


\bibitem{ROOT}
I.Antcheva et al., 
\textit{ 
ROOT — A C++ framework for petabyte data storage, statistical analysis and visualization},
Computer Physics Communications (2009), vol. 180, no. 12.

\bibitem{HistFactory}
Cranmer, Kyle and Lewis, George and Moneta, Lorenzo and Shibata, Akira and Verkerke, Wouter,
\textit{ 
HistFactory: A tool for creating statistical models for use with RooFit and RooStats},
CERN-OPEN-2012-016.

\bibitem{CaloTerapie}
Agenzia Nazionale Stampa Associata, 
\textit{Coronavirus: Calano malati in terapia intensiva, è la prima volta. In Lombardia in giro con le mascherine},
\href{https://www.ansa.it/canale_saluteebenessere/notizie/sanita/2020/04/04/coronavirus-_29e301b7-fd53-405c-9e5d-92f907057932.html}{Salute\&Benessere, 05 Aprile 2020.}

\bibitem{R0}
Ministero della Salute, \textit{Covid-19, Ministro Speranza: ``Vicini a R con zero inferiore a 1, ma la sfida non è vinta'' },
\href{http://www.salute.gov.it/portale/news/p3_2_1_1_1.jsp?lingua=italiano&menu=notizie&p=dalministero&id=4429}{News, 9 Aprile 2020.}

\end{thebibliography}


\newpage
\begin{appendices}
\input{sections/Appendix}
\end{appendices}

\end{document}
